A Generalized Sphere Theorem for Positively Curved Combinatorial 3-Manifolds

### 2013-06-13 paper/paper.tex
bit of editing on abstract. worked on captions and other stuff for figures

\noindent Interestingly, while the statement of Theorem \ref{thm:discrete_BM} uses edge-diameter, its proof relies on expanding the set of paths under consideration to include those which contain not only edges, but also other types of PL-paths between vertices.

\subsection{Hops and Jumps}
The first new type of path is called a {\em hop}.

@@

A small Python program was created to examine each manifold in the census and compute its diameter. See Figure \ref{fig:type_statistics} for a plot of the number of manifolds by topological type and diameter. As claimed, every manifold with diameter greater than $J$ is a 3-sphere. The corresponding data using the coarser-grained edge-diameter can be found in Figure \ref{fig:type_statistics_edges}. Note the existence of $3$-manifolds with edge-diameter greater than half the maximum allowed edge-diameter and which are {\em not} homeomorphic to the 3-sphere. In particular, there are positively curved combinatorial 3-manifolds homeomorphic to $\mathbb{RP}^3$, $L(3,1)$ and $L(4,1)$ which have edge-diameter three.

>>>>

\noindent Interestingly, while the statement of Theorem \ref{thm:discrete_BM} uses edge-diameter, its proof relies on expanding the set of paths under consideration to include those which contain not only edges, but also other types of PL-paths between vertices. In this work, this enlarged set of paths will be crucial to obtaining a discrete result fully analogous to the classical generalized sphere theorem.

\section{Hops and Jumps}
The first new type of path is called a {\em hop}.

@@

A small Python program (available on request) was created to examine each manifold in the census and compute its diameter. See Figure \ref{fig:type_statistics} for a plot of the number of manifolds by topological type and diameter. As claimed, every manifold with diameter greater than $J$ is a 3-sphere. The corresponding data using the coarser-grained edge-diameter can be found in Figure \ref{fig:type_statistics_edges}. Note the existence of $3$-manifolds with edge-diameter greater than half the maximum allowed edge-diameter and which are {\em not} homeomorphic to the 3-sphere. In particular, there are positively curved combinatorial 3-manifolds homeomorphic to $\mathbb{RP}^3$, $L(3,1)$ and $L(4,1)$ which have edge-diameter three.
